Powering Hidden Markov Model by Neural Network based Generative Models

### 2019-11-14 manuscript/main.tex
modify table
minor change

\begin{table}
  \caption{Test accuracy table for $39$ dimensional features and folded $39$ Phonemes }\label{tab:acc-classification39f_a}
  \centering  
  \begin{tabular}{l|c|c|c}
    \toprule
    {Model} &  K=1 &  K=3 &  K=5  \\  \midrule
    GMM-HMM & $62.3\%$ &  $68.0\%$ &  $68.7\%$  \\ \midrule
    GenHMM & $76.7\%$ & $77.7\%$ &  $77.7\%$ \\ 
    \bottomrule                                                                  
  \end{tabular}
\end{table}

\begin{table}
  \caption{Test accuracy table for $39$ dimensional features and $61$ Phonemes}\label{tab:acc-classification39f_b}
  \centering  
  \begin{tabular}{l|c|c|c} \toprule
    {Model} &  K=1 &  K=3 &  K=5
    \\ \midrule
    GMM-HMM & $53.6\%$ &  $59.6\%$ & $61.9\%$  \\ \midrule
    GenHMM & $69.5\%$ & $70.6\%$ & $70.7\%$   \\ 
    \bottomrule
  \end{tabular}
  \vspace{0.2cm}
\end{table}
We firstly show the phoneme classification using 39 dimensional MFCC features (MFCC coefficients, deltas, and delta-deltas), to validate one possible usage of our proposed model. Since generative training is carried out in our experiments, GMM-HMM is trained and tested as a reference model in our experiments. Training and testing of GMM-HMM is in the same condition as GenHMMs are trained and tested. Dataset usage for GenMM and GMM-HMM is the same, and number of states for GMM-HMM is the same as that for GenHMM in modeling each phoneme. Apart from setting the reference model, we also run the experiment comparisons with different total number of mixture components.

@@

\begin{table}
  \caption{Test accuracy table for $13$ dimensional features and Folded $39$ Phonemes}\label{tab:acc-classification13f_a}
  \centering  
  \begin{tabular}{l|c|c|c}
    \toprule
    {Model} &  K=1 &  K=3 &  K=5  \\  \midrule
    GMM-HMM & $48.5\%$ &  $51.2\%$ &  $52.4\%$  \\ \midrule
    GenHMM & $61.1\%$ & $62.1\%$ & $62.1\%$   \\ 
    \bottomrule                                                                  
  \end{tabular}
\end{table}
\begin{table}
  \caption{Test accuracy table for $13$ dimensional features and $61$
    Phonemes}\label{tab:acc-classification13f_b}
  \centering
  \begin{tabular}{l|c|c|c}
    \toprule
    {Model} &  K=1 &  K=3 &  K=5
    \\ \midrule
    GMM-HMM & $37.1\%$ &  $40.6\%$ & $42.2\%$  \\ \midrule
    GenHMM & $50.3\%$ & $51.0\%$ & $52.3\%$   \\ 
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \caption{Test accuracy table for $39$ dimensional features and folded $39$ phonemes.}\label{tab:acc-classification39f_a}
  \centering  
  \begin{tabular}{l|c|c|c}
    \toprule
    {Model} &  K=1 &  K=3 &  K=5  \\  \midrule
    GMM-HMM & $62.3\%$ &  $68.0\%$ &  $68.7\%$  \\ \midrule
    GenHMM & $76.7\%$ & $77.7\%$ &  $77.7\%$ \\ 
    \bottomrule                                                                  
  \end{tabular}
\end{table}

\begin{table}
  \caption{Test accuracy table for $39$ dimensional features and $61$ phonemes.}\label{tab:acc-classification39f_b}
  \centering  
  \begin{tabular}{l|c|c|c} \toprule
    {Model} &  K=1 &  K=3 &  K=5
    \\ \midrule
    GMM-HMM & $53.6\%$ &  $59.6\%$ & $61.9\%$  \\ \midrule
    GenHMM & $69.5\%$ & $70.6\%$ & $70.7\%$   \\ 
    \bottomrule
  \end{tabular}
  \vspace{0.2cm}
\end{table}
We firstly show the phoneme classification using 39 dimensional MFCC features (MFCC coefficients, deltas, and delta-deltas), to validate one possible usage of our proposed model. Since generative training is carried out in our experiments, GMM-HMM is trained and tested as a reference model in our experiments. Training and testing of GMM-HMM is in the same condition as GenHMMs are trained and tested. Dataset usage for GenMM and GMM-HMM is the same, and number of states for GMM-HMM is the same as that for GenHMM in modeling each phoneme. Apart from setting the reference model, we also run the experiment comparisons with different total number of mixture components.

@@

\begin{table}
  \caption{Test accuracy table for $13$ dimensional features and folded $39$ phonemes.}\label{tab:acc-classification13f_a}
  \centering  
  \begin{tabular}{l|c|c|c}
    \toprule
    {Model} &  K=1 &  K=3 &  K=5  \\  \midrule
    GMM-HMM & $48.5\%$ &  $51.2\%$ &  $52.4\%$  \\ \midrule
    GenHMM & $61.1\%$ & $62.1\%$ & $62.1\%$   \\ 
    \bottomrule                                                                  
  \end{tabular}
\end{table}
\begin{table}
  \caption{Test accuracy table for $13$ dimensional features and $61$
    phonemes.}\label{tab:acc-classification13f_b}
  \centering
  \begin{tabular}{l|c|c|c}
    \toprule
    {Model} &  K=1 &  K=3 &  K=5
    \\ \midrule
    GMM-HMM & $37.1\%$ &  $40.6\%$ & $42.2\%$  \\ \midrule
    GenHMM & $50.3\%$ & $51.0\%$ & $52.3\%$   \\ 
    \bottomrule
  \end{tabular}
\end{table}
